Dendritic Ca2+ as a Predictor of Stimulus Perception and Behavior

### 2017-09-13 presentation_Naoya/demo.tex
asd

\section{Univariate Analysis}

\begin{frame}[fragile]{SVM - What is an SVM?}
\begin{columns}[T,onlytextwidth]
\column{0.5\textwidth}
\only<1->{
\begin{center}
\begin{figure}
      \includegraphics[height=0.6\textwidth]{svm_exp1.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\column{0.5\textwidth}
\only<4->{
SMVs...
\begin{itemize}
\item are a staple of machine learning
\item have a regularization parameter that can combat overfitting
\item are good for small samples with many features (in theory)
\end{itemize}
}
\end{columns}
	\begin{columns}[T,onlytextwidth]
    \column{0.5\textwidth}
    	\only<2->{
      \begin{figure}
      \includegraphics[height=0.7\textwidth]{svm_exp2.png}
      \end{figure}}

    \column{0.5\textwidth}
		\only<3->{
      \begin{figure}
      \includegraphics[height=0.7\textwidth]{svm_exp3.png}
      \end{figure}}

@@

\begin{frame}[fragile]{Rank Order Correlation}
\only<+->{
We want to quantify the similarity between two rank orders of dendrites $R$ and $Q$, which both have length $n$.}

@@

\only<+->{
$$
\rho(R,Q) = 1 - \frac{6\sum_i^nD_i^2}{n(n	^2-1)}
$$
}

\only<+->{
Problem: Many of the dendrites are not significant for classification but affect $\rho$ greatly. We would like to be able to \textbf{weight our} $\mathbf{R}$'s and $\mathbf{Q}$'s.}
\end{frame}

@@

\section{Multivariate SMV Analysis}

>>>>

\section{Univariate Analysis}
\begin{frame}[fragile]{SVM - What is an SVM?}
\begin{columns}[T,onlytextwidth]
\column{0.5\textwidth}
\begin{center}
\begin{figure}
      \includegraphics[height=0.6\textwidth]{machine_learning.png}
      \caption*{Figure - xkcd}
	\end{figure}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\column{0.5\textwidth}
SMV...
\begin{itemize}
\item is a supervised learning algorithm
\begin{itemize}
\item uses labelled data
\end{itemize}
\item has a regularization parameter that can combat overfitting
\item is good for small samples with many features (in theory)
\end{itemize}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM - What is an SVM?}
\only<1->{
Works on linearily separable and nonseparable data of \textbf{arbitrary dimension}}
\begin{columns}[T,onlytextwidth]
\column{0.5\textwidth}
\begin{center}
\only<2->{
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_sep.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\column{0.5\textwidth}
\begin{center}
\only<3->{
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_nonsep.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM - What is an SVM? Linearily Separable Case}
\begin{columns}[T,onlytextwidth]
\column{0.4\textwidth}
\begin{center}
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
There are many separating hyperplanes, but which one is best?
\end{center}
\column{0.55\textwidth}
\begin{center}
\begin{figure}
      \includegraphics[height=0.9\textwidth]{svm_hyper.png}
	\end{figure}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM - What is an SVM? The Margin}
\begin{columns}[T,onlytextwidth]
\column{0.4\textwidth}
\only<+->{
\begin{center}
\bigskip
\bigskip
\bigskip
The one that maximizes the hyperplanes' distance from the nearest datapoints of either class while classifying all data correctly - \textbf{the margin}
\end{center}}
\column{0.55\textwidth}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.9\textwidth]{svm_mar.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM - What is an SVM? The Margin}
\begin{columns}[T,onlytextwidth]
\column{0.4\textwidth}
\begin{center}
\only<+->{
The hyperplane is given by
\begin{align*}
g(\mathbf{x}) = \mathbf{w^Tx + b}
\end{align*}}
\only<+->{
It turns out that the margin is given by $\frac{2}{||w||}$ and we maximize it by minimizing
\begin{align*}
\frac{1}{2}||\mathbf{w}||_2^2
\end{align*}}
\only<+->{
under the constraint that \textbf{all data are classified correctly}.}
\end{center}
\column{0.55\textwidth}
\begin{center}
\begin{figure}
      \includegraphics[height=0.9\textwidth]{svm_mar.png}
	\end{figure}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
\begin{columns}[T,onlytextwidth]
\column{0.5\textwidth}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_nonsep.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\column{0.5\textwidth}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_cl.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
\only<+->{
We permit Errors, but still penalize them!}
\begin{columns}[T,onlytextwidth]
\column{0.5\textwidth}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_nonsep_mar.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\column{0.5\textwidth}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_nonsep_err.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
\begin{columns}[T,onlytextwidth]
\column{0.5\textwidth}
\only<+->{
Instead of $\frac{1}{2}||\mathbf{w}||_2^2$ we now minimize
\begin{align*}
\frac{1}{2}||\mathbf{w}||_2^2 + C\sum_{i=1}^n \xi_i}
\end{align*}
\only<+->{
where $\xi_i$ is the distance of a data point from their correct decision region.}

\only<+->{
\textbf{The parameter C lets us now control the tradeoff between the generalization and training error (overfitting).}}
\column{0.5\textwidth}
\begin{center}
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_nonsep_err.png}
	\end{figure}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

@@

\begin{frame}[fragile]{Rank Order Correlation}
\only<+->{
We want to quantify the similarity between two rank orders of dendrites $R$ and $Q$, which both have length $n$. For example, we would like to see whether similar dendrites react to similar stimuli.}

@@

\only<+->{
We use a modified version of that because we usually have \textbf{many uninformative dendrites} that can skew the result (their exact rank is unimportant).}
\end{frame}

@@

\section{Multivariate SVM Analysis}
